\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=2.2cm]{geometry}

% Font encoding / symbols (fixes £ rendering in PDFLaTeX)
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp} % provides \textsterling and other TS1 symbols

% Very standard, boring serif font
\usepackage{newtxtext}
\usepackage{newtxmath}

\usepackage{microtype}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    pdftitle={Short-Form Postnuptial Agreement},
    pdfauthor={Working Draft for Solicitor Review}
}

% More "legal doc" feel: smaller type, tighter leading
\setstretch{1.05}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}

% Conservative headings
\titleformat{\section}{\normalsize\bfseries}{\thesection.}{0.6em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{0.6em}{}

% Lists: tighter spacing, more formal
\setlist[itemize]{leftmargin=1.8em, itemsep=0.2em, topsep=0.4em}
\setlist[enumerate]{leftmargin=1.8em, itemsep=0.25em, topsep=0.4em}

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

% Parties / details
\newcommand{\PartyOne}{Asfand Yar Qazi}
\newcommand{\PartyTwo}{Aisha Iftikhar}
\newcommand{\CurrentHome}{33 Craighill Road, Leicester LE2 3FD}
\newcommand{\ReplacementHome}{155 Jamie Marcus Way, Oadby, Leicester, LE2 4WB}
\newcommand{\MarriageDate}{3 November 2017}
\newcommand{\MarriagePlace}{Redbridge Town Hall, Ilford}

\begin{document}

\begin{center}
    {\Large\bfseries SHORT-FORM POSTNUPTIAL AGREEMENT}\\[0.35em]
    {\normalsize Working Draft for Solicitor Review}
\end{center}

\vspace{0.6em}

\noindent\textbf{Important note:} This is a practical working draft intended for solicitor review. It is designed to record the Parties' current wishes and intentions and to carry as much weight as the law of England and Wales may permit. For greater legal weight, it should be reviewed by a family solicitor and each Party should obtain independent legal advice before signing.

\vspace{0.9em}

\begin{center}
    {\large\bfseries POSTNUPTIAL AGREEMENT}
\end{center}

\noindent\textbf{THIS AGREEMENT IS MADE AS A DEED} on \rule{7cm}{0.4pt}

\section*{BETWEEN}

\noindent\textbf{\PartyOne} of \CurrentHome\ (\textbf{Party 1}); and

\noindent\textbf{\PartyTwo} of \CurrentHome\ (\textbf{Party 2})

\noindent (each a \textbf{Party} and together the \textbf{Parties}).

\section*{BACKGROUND}

\begin{enumerate}[label=\arabic*., leftmargin=1.8em]
    \item The Parties were married on \textbf{\MarriageDate} at \textbf{\MarriagePlace}.
    \item The Parties currently live together at \textbf{\CurrentHome}.
    \item The Parties have two children of the family:
    \begin{itemize}[leftmargin=1.8em]
        \item \textbf{Aynie Qazi}, born \textbf{26/05/2015}
        \item \textbf{Ayoub Qazi}, born \textbf{10/07/2019}
    \end{itemize}
    \item The Parties currently own the family home at \textbf{\CurrentHome}, with an approximate value of \textbf{\textsterling 420,000} and an approximate mortgage of \textbf{\textsterling 290,000}, in joint names.
    \item The Parties intend to complete the purchase of a replacement family home at \textbf{\ReplacementHome} on or about \textbf{29 June 2026} (the \textbf{Replacement Home}) for a purchase price of \textbf{\textsterling 451,950}.
    \item The Parties intend that this Agreement shall regulate their financial arrangements only from the completion date of the move from the Current Home to the Replacement Home, namely the date on which the sale of the Current Home completes and the purchase of the Replacement Home completes and the Parties move from the Current Home into the Replacement Home (the \textbf{Move Date}). For the avoidance of doubt, this Agreement is not intended to regulate any period before the Move Date.
    \item The Parties wish to record their mutual wishes and intentions regarding financial arrangements in the event of separation or permanent breakdown of the marriage after the Move Date, with the aim of reducing uncertainty, dispute and litigation.
    \item The Parties acknowledge that the welfare and needs of the children remain important and that the court retains jurisdiction in relation to children and financial matters as required by law.
    \item The Parties intend this Agreement to be persuasive and to carry as much weight as the law of England and Wales may permit.
    \item The Parties confirm that they have had adequate opportunity to reflect upon the terms of this Agreement and to obtain independent legal advice before signing it.
\end{enumerate}

\section*{PERSONAL AND FINANCIAL DISCLOSURE}

\begin{enumerate}[label=\arabic*., start=11, leftmargin=1.8em]
    \item The Parties confirm that, to the best of their present knowledge, each has disclosed to the other sufficient information concerning his or her assets, liabilities, income and relevant financial circumstances to enable the fairness of this Agreement to be assessed.
    \item The Parties' current headline financial circumstances are as follows.
\end{enumerate}

\subsection*{Party 1 --- \PartyOne}

\begin{itemize}[leftmargin=1.8em]
    \item Occupation: software engineer
    \item Gross income: approximately \textbf{\textsterling 90,000 per annum}
    \item Cash: approximately \textbf{\textsterling 1,000}
    \item ISA: approximately \textbf{\textsterling 5,652}
    \item Pension: none declared
    \item Business interests: none declared
    \item Debts/liabilities: none declared
\end{itemize}

\subsection*{Party 2 --- \PartyTwo}

\begin{itemize}[leftmargin=1.8em]
    \item Occupation: self-employed art tutor
    \item Income: approximately \textbf{\textsterling 300 per calendar month}
    \item Cash: approximately \textbf{\textsterling 300}
    \item Car: approximately \textbf{\textsterling 4,000}
    \item Gold: approximately \textbf{\textsterling 500}
    \item Pension: none declared
    \item Business interests: none declared
    \item Debts/liabilities: none declared
\end{itemize}

\subsection*{Children's assets / costs}

\begin{itemize}[leftmargin=1.8em]
    \item Daughter JISA: approximately \textbf{\textsterling 2,174}
    \item Son JISA: approximately \textbf{\textsterling 2,000}
    \item Child health-related medicines/treatments: approximately \textbf{\textsterling 200 per calendar month} on average
\end{itemize}

\begin{enumerate}[label=\arabic*., start=13, leftmargin=1.8em]
    \item Each Party confirms that the information stated in this Agreement and in the schedules is intended as honest disclosure for the purposes of this Agreement, subject to correction or supplementation if reasonably required.
    \item Each Party further confirms that, as at the date of signing, he or she does not knowingly withhold any material asset, liability or source of income relevant to the fairness of this Agreement.
\end{enumerate}

\section*{PURPOSE AND PRINCIPLES}

\begin{enumerate}[label=\arabic*., start=15, leftmargin=1.8em]
    \item The Parties agree that this Agreement is intended to:
    \begin{itemize}[leftmargin=1.8em]
        \item protect identified separate property;
        \item preserve certain gifts and inheritances from later claim where fair to do so;
        \item recognise the housing and day-to-day needs of the children;
        \item record the Parties' intended approach to support and housing if the marriage breaks down;
        \item reduce the risk of litigation and opportunistic conduct.
    \end{itemize}
    \item The Parties further agree that this Agreement is based on what they presently believe to be a fair arrangement having regard to:
    \begin{itemize}[leftmargin=1.8em]
        \item the needs of the Parties;
        \item the needs of the children;
        \item the present disparity in income;
        \item the importance of stable housing for the children;
        \item the intention that Party 2 should not be left without practical housing provision if separation occurs;
        \item the intention that Party 1's agreed separate property should remain his, and Party 2's agreed separate property should remain hers.
    \end{itemize}
\end{enumerate}

\section*{DEFINITIONS}

\begin{longtable}{p{0.28\textwidth}p{0.67\textwidth}}
\toprule
\textbf{Term} & \textbf{Meaning} \\
\midrule
Agreement & this deed together with its schedules. \\
Current Home & \CurrentHome. \\
Replacement Home & \ReplacementHome. \\
Move Date & the completion date on which the sale of the Current Home completes and the purchase of the Replacement Home completes and the Parties move from the Current Home into the Replacement Home. \\
Permanent Breakdown & separation followed by divorce proceedings, judicial separation, or such other clear and sustained breakdown of the marriage as makes reconciliation no longer realistic. \\
Separate Property & property intended by this Agreement to remain the separate property of one Party. \\
Joint Property & property not expressly identified as Separate Property. \\
Written Notice & any written communication capable of being retained and produced, including a signed letter, email, text message or messaging-app communication. \\
Transition Period & the period of three months beginning on the date on which either Party gives Written Notice to the other that the marriage is over. \\
Moved Out Permanently & Party 1 has begun living at another residence on a settled basis as his main home; temporary returns for childcare, practical arrangements, emergencies or short visits shall not of themselves prevent this condition being satisfied. \\
Monthly Household Contribution & the monthly payment presently fixed at \textbf{\textsterling 3,500} pursuant to this Agreement, subject to review in accordance with this Agreement. \\
Cohabitation & Party 2 living in the family home with a partner on a settled basis, whether married to that partner or not. \\
\bottomrule
\end{longtable}

\section*{SEPARATE PROPERTY}

\begin{enumerate}[label=\arabic*., start=17, leftmargin=1.8em]
    \item The following shall be treated as \textbf{Party 1's Separate Property}:
    \begin{itemize}[leftmargin=1.8em]
        \item his ISA, presently valued at approximately \textbf{\textsterling 5,652};
        \item the sum of \textbf{\textsterling 20,000} to be held after completion in a separate account as ring-fenced personal savings (the \textbf{Ring-Fenced Savings});
        \item any property expressly agreed in writing after the date of this Agreement to be his Separate Property;
        \item external inheritances and gifts received by him, whether before or after this Agreement, unless clearly converted into Joint Property by written agreement.
    \end{itemize}
    \item The following shall be treated as \textbf{Party 2's Separate Property}:
    \begin{itemize}[leftmargin=1.8em]
        \item her car, presently valued at approximately \textbf{\textsterling 4,000};
        \item her gold, presently valued at approximately \textbf{\textsterling 500};
        \item external inheritances and gifts received by her, whether before or after this Agreement, which are intended to be ring-fenced to her and/or for the children and not for Party 1;
        \item any property expressly agreed in writing after the date of this Agreement to be her Separate Property.
    \end{itemize}
    \item Past gifts made to Party 2 by Party 1 or by members of Party 1's family are agreed to be completed gifts and shall not be reclaimed.
    \item Party 1 may, by clear written instruction, irrevocably gift any inheritance or gift received by him, or any part thereof, to the children, after which he shall retain no claim to the gifted portion.
    \item The Parties acknowledge that a court may still consider needs, fairness and the interests of the children, but they intend that the Separate Property identified above should, so far as lawful and fair, remain outside later division.
\end{enumerate}

\section*{JOINT PROPERTY AND FAMILY HOME}

\begin{enumerate}[label=\arabic*., start=22, leftmargin=1.8em]
    \item The Current Home is presently treated as Joint Property.
    \item The Parties intend that the Replacement Home will be owned in their joint names and, unless later agreed in writing, beneficial ownership is intended to be joint.
    \item The deposit for the Replacement Home is intended to be funded from the proceeds of sale of the Current Home.
    \item In the event of Permanent Breakdown, the Parties' present housing intention is that:
    \begin{itemize}[leftmargin=1.8em]
        \item the children are to remain primarily living with Party 2 in the family home, subject always to safety, welfare, affordability and any court order;
        \item Party 1 may remain in the home for up to six months after he gives or receives Written Notice that the marriage is over, or until he has secured and moved into his own place, whichever occurs first, unless safety concerns or serious conflict require earlier departure;
        \item if Party 1 forms a new relationship and seeks to continue living in the home after separation, the Parties shall treat that circumstance as requiring immediate review of occupation arrangements;
        \item the longer-term goal is for the mortgage and legal title to the Replacement Home to be transferred into Party 2's sole name when feasible and financially responsible.
    \end{itemize}
    \item The joint ownership of the Replacement Home shall continue until the home is sold or the mortgage is transferred into Party 2's sole name and any related transfer of legal title is completed.
\end{enumerate}

\section*{SEPARATION, TRANSITION AND SUPPORT}

\begin{enumerate}[label=\arabic*., start=27, leftmargin=1.8em]
    \item Either Party may give Written Notice to the other that the marriage is over.
    \item Such Written Notice shall begin the Transition Period of three months.
    \item During the Transition Period, the Parties shall use good faith endeavours to put in place practical arrangements for:
    \begin{itemize}[leftmargin=1.8em]
        \item separate living arrangements;
        \item separate finances;
        \item implementation of post-separation financial arrangements;
        \item review of practical arrangements concerning the children.
    \end{itemize}
    \item The Parties intend that full practical separation shall be achieved within the Transition Period.
    \item The Monthly Household Contribution shall become payable on the earlier of:
    \begin{itemize}[leftmargin=1.8em]
        \item the date on which Party 1 has Moved Out Permanently; or
        \item the expiry of the Transition Period.
    \end{itemize}
    \item Until the Monthly Household Contribution becomes payable, Party 1 shall remain responsible for maintaining the household finances substantially as at present, unless otherwise agreed in writing.
    \item If Party 1 remains physically in the home after Written Notice for any part of the Transition Period, the Parties intend that he shall continue meeting the household costs during that period.
    \item The Monthly Household Contribution is presently fixed at \textbf{\textsterling 3,500 per calendar month}.
    \item The Monthly Household Contribution shall be paid by bank transfer to Party 2 on the \textbf{last Thursday of each month}.
    \item If the due date falls on a bank holiday or payment cannot reasonably be made on that date due to banking-system disruption, payment shall be made on the next working day.
    \item For the purposes of this Agreement, household costs include, without limitation:
    \begin{itemize}[leftmargin=1.8em]
        \item mortgage payments;
        \item buildings and contents insurance;
        \item council tax;
        \item utilities;
        \item broadband and essential communications;
        \item TV licence;
        \item essential repairs and maintenance;
        \item groceries;
        \item children's ordinary school-related costs;
        \item children's ordinary clothing;
        \item reasonable local transport costs for the children;
        \item ordinary child health and medicine costs.
    \end{itemize}
    \item Late payment shall be treated as serious. Party 2 shall first give written notice of non-payment and Party 1 shall have a grace period of five working days, after which legal remedies remain available.
\end{enumerate}

\section*{REVIEW OF SUPPORT AND AFFORDABILITY}

\begin{enumerate}[label=\arabic*., start=38, leftmargin=1.8em]
    \item Either Party may request a review of the Monthly Household Contribution at any time.
    \item If more than six months have passed since the last review, the other Party shall engage in a review in good faith upon written request.
    \item If fewer than six months have passed since the last review, a further review may still take place by agreement.
    \item Until a new figure is agreed in writing by both Parties, or ordered by a court, the existing Monthly Household Contribution shall continue to apply.
    \item A review shall in particular be triggered by any of the following:
    \begin{itemize}[leftmargin=1.8em]
        \item a reduction of Party 1's gross income by 25\% or more from the current baseline of \textbf{\textsterling 90,000 per annum} lasting for at least three months;
        \item loss of Party 1's employment or equivalent loss of earnings;
        \item Party 2 becoming realistically able to remortgage or take transfer of the Replacement Home into her sole name;
        \item Party 2's remarriage or Cohabitation;
        \item a material change in the children's needs;
        \item any material change in housing costs or mortgage obligations;
        \item long-term illness or inability of either Party to work;
        \item receipt of a significant inheritance or gift;
        \item any credible risk of debt, default, insolvency or bankruptcy arising if the current arrangements continue unchanged.
    \end{itemize}
    \item In any review, the Parties shall act in good faith and shall consider income, expenditure, housing costs, the children's needs and the objective of avoiding debt, default, insolvency and bankruptcy for either Party.
\end{enumerate}

\section*{COHABITATION, REMARRIAGE AND CHILDREN-RELATED REVIEW}

\begin{enumerate}[label=\arabic*., start=44, leftmargin=1.8em]
    \item If Party 2 remarries or enters Cohabitation, this shall trigger an immediate review of:
    \begin{itemize}[leftmargin=1.8em]
        \item the Monthly Household Contribution;
        \item the arrangements for removing Party 1 from the joint mortgage and legal title at the earliest financially sensible opportunity;
        \item the practical and financial arrangements concerning the children.
    \end{itemize}
    \item The Parties acknowledge that any review concerning the children must remain subject to the children's welfare and the jurisdiction of the court.
    \item The Parties intend that remarriage or Cohabitation shall not automatically terminate support, but may justify a reduction or restructuring of support having regard to fairness, needs, the children's arrangements and the Parties' respective financial circumstances.
    \item For the avoidance of doubt, nothing in this Agreement gives Party 1 any additional beneficial share in the Replacement Home by reason only of Party 2's remarriage or Cohabitation.
\end{enumerate}

\section*{REPLACEMENT HOME, REMORTGAGE AND SALE}

\begin{enumerate}[label=\arabic*., start=48, leftmargin=1.8em]
    \item Party 2 intends to make repeated reasonable attempts to remortgage or otherwise secure transfer of the Replacement Home into her sole name when a lender affordability assessment makes that realistically possible.
    \item Party 1 shall reasonably cooperate with any financially responsible process aimed at his removal from the joint mortgage and legal title, including at the next suitable remortgage opportunity if appropriate.
    \item The Parties intend that the home should be retained where reasonably possible for the children's stability, but not at the cost of debt, default, insolvency or bankruptcy risk for either Party.
    \item If the current arrangements create a credible risk of mortgage arrears, household-payment default, unsustainable borrowing, insolvency or bankruptcy for either Party, the Parties shall first undertake a good-faith review of support and housing arrangements to seek a sustainable alternative.
    \item If, after such review, no sustainable arrangement can be agreed or implemented in time to avoid debt or default risk, the home shall be sold and the Parties shall take all necessary steps promptly to effect the sale.
    \item If sale becomes necessary, the Parties intend that the division of net sale proceeds shall first be negotiated in good faith, with \textbf{50\% / 50\%} as the fallback if no agreement is reached.
\end{enumerate}

\section*{CHILDREN}

\begin{enumerate}[label=\arabic*., start=54, leftmargin=1.8em]
    \item The Parties agree that financial and practical provision for the children should be dealt with fairly and in accordance with law.
    \item Child arrangements are intended to remain flexible and are not fixed by this Agreement.
    \item Any future arrangements concerning the children may need to be resolved by agreement, mediation, legal advice, arbitration or family court if necessary, by reference to the children's welfare at that time.
\end{enumerate}

\section*{WILLS AND DEATH}

\begin{enumerate}[label=\arabic*., start=57, leftmargin=1.8em]
    \item Neither Party currently has a will.
    \item The Parties acknowledge that, if inheritance intentions are to be reflected properly, each should make a will as soon as reasonably practicable after taking advice.
    \item This Agreement is not a substitute for a will.
    \item If, following Permanent Breakdown, either Party should die, the other Party shall not make any claim against the deceased's estate except as consistent with this Agreement and applicable law.
\end{enumerate}

\section*{CONFIDENTIALITY}

\begin{enumerate}[label=\arabic*., start=61, leftmargin=1.8em]
    \item The Parties agree to keep confidential any private financial information exchanged for the purposes of this Agreement, save where disclosure is reasonably required for legal advice, implementation of this Agreement, dispute resolution, court proceedings, tax, lending, regulatory compliance or other legal obligation.
\end{enumerate}

\section*{REVIEW OF THIS AGREEMENT}

\begin{enumerate}[label=\arabic*., start=62, leftmargin=1.8em]
    \item The Parties intend that this Agreement should be reviewed with the benefit of legal advice if any of the following occurs:
    \begin{itemize}[leftmargin=1.8em]
        \item acquisition of the Replacement Home;
        \item significant change in mortgage obligations or housing arrangements;
        \item a reduction in Party 1's income by 25\% or more;
        \item long-term illness or inability to work;
        \item receipt of a significant inheritance or gift;
        \item Party 2's remarriage or Cohabitation;
        \item any material change affecting the children's needs;
        \item any move outside England and Wales.
    \end{itemize}
\end{enumerate}

\section*{INDEPENDENT LEGAL ADVICE AND ACKNOWLEDGEMENT}

\begin{enumerate}[label=\arabic*., start=63, leftmargin=1.8em]
    \item The Parties acknowledge that:
    \begin{itemize}[leftmargin=1.8em]
        \item this Agreement should be reviewed by a family solicitor;
        \item each Party should obtain separate and independent legal advice before signing;
        \item written confirmation or certificates of such advice should be retained with the signed document if available.
    \end{itemize}
    \item Each Party acknowledges that independent legal advice and full disclosure are important if this Agreement is later to be given substantial weight.
    \item Each Party confirms that he or she is entering into this Agreement freely, voluntarily and without pressure from the other Party or any third party.
    \item Each Party confirms that he or she understands the broad nature and effect of the rights being regulated by this Agreement.
\end{enumerate}

\section*{GENERAL}

\begin{enumerate}[label=\arabic*., start=67, leftmargin=1.8em]
    \item This Agreement is intended to record the Parties' present wishes and intentions and to be persuasive to the maximum extent permitted by the law of England and Wales.
    \item In the event of Permanent Breakdown, the Parties intend that their financial rights and obligations shall, so far as lawful and fair, be governed by this Agreement.
    \item No variation of this Agreement shall be effective unless made in writing and signed by both Parties as a deed or in such other legally effective written form as their solicitors may advise.
    \item This Agreement constitutes the entire agreement between the Parties concerning its subject matter and supersedes prior discussions or understandings relating to that subject matter.
    \item This Agreement shall be governed by and interpreted according to the law of England and Wales, and disputes arising under it shall be subject to the jurisdiction of the courts of England and Wales.
    \item The Parties shall each bear their own costs of preparing and obtaining advice upon this Agreement unless otherwise agreed.
\end{enumerate}

\section*{EXECUTION}

\noindent\textbf{IN WITNESS OF WHICH} the Parties have signed this Agreement as a deed on the day and year first above written.

\vspace{1.0em}

\begin{tabularx}{\textwidth}{|Y|Y|}
\hline
\multicolumn{2}{|l|}{\textbf{Executed as a deed by Party 1}} \\
\hline
Signature of Party 1 & \\[1.0cm]
\hline
Name & \PartyOne \\[0.4cm]
\hline
In the presence of witness: & \\
\hline
Witness signature & \\[0.9cm]
\hline
Name of witness & \\[0.8cm]
\hline
Address & \\[1.2cm]
\hline
Occupation & \\[0.8cm]
\hline
Date & \\[0.8cm]
\hline
\end{tabularx}

\vspace{1.2em}

\begin{tabularx}{\textwidth}{|Y|Y|}
\hline
\multicolumn{2}{|l|}{\textbf{Executed as a deed by Party 2}} \\
\hline
Signature of Party 2 & \\[1.0cm]
\hline
Name & \PartyTwo \\[0.4cm]
\hline
In the presence of witness: & \\
\hline
Witness signature & \\[0.9cm]
\hline
Name of witness & \\[0.8cm]
\hline
Address & \\[1.2cm]
\hline
Occupation & \\[0.8cm]
\hline
Date & \\[0.8cm]
\hline
\end{tabularx}

\newpage
\section*{Schedule 1 --- Property and Liabilities of Party 1}

\subsection*{Property of \PartyOne}
\begin{itemize}[leftmargin=1.8em]
    \item Cash: approximately \textsterling 1,000
    \item ISA: approximately \textsterling 5,652
    \item Ring-Fenced Savings: \textsterling 20,000 to be held after completion in a separate account
    \item Any external inheritances and gifts intended to remain his Separate Property
\end{itemize}

\subsection*{Liabilities of \PartyOne}
\begin{itemize}[leftmargin=1.8em]
    \item None declared at present
\end{itemize}

\newpage
\section*{Schedule 2 --- Property and Liabilities of Party 2}

\subsection*{Property of \PartyTwo}
\begin{itemize}[leftmargin=1.8em]
    \item Cash: approximately \textsterling 300
    \item Car: approximately \textsterling 4,000
    \item Gold: approximately \textsterling 500
    \item Any external inheritances and gifts intended to remain her Separate Property and/or for the children
\end{itemize}

\subsection*{Liabilities of \PartyTwo}
\begin{itemize}[leftmargin=1.8em]
    \item None declared at present
\end{itemize}

\newpage
\section*{Schedule 3 --- Certificate of Independent Specialist Legal Adviser for Party 1}

\noindent I, \rule{5cm}{0.4pt} of \rule{8cm}{0.4pt}, certify as follows:

\begin{enumerate}[label=\arabic*., leftmargin=1.8em]
    \item I am a duly qualified solicitor/barrister (delete as appropriate) of the Senior Courts of England and Wales.
    \item Prior to \PartyOne\ entering into the Agreement between Party 1 and \PartyTwo\ to which this certificate is annexed:
    \begin{enumerate}[label=(\alph*), leftmargin=1.8em]
        \item I explained to Party 1 the meaning and importance of the terms of the Agreement in such a way that I believe that he has understood them, and he confirmed to me that he does understand them;
        \item I advised Party 1 as to the effect of the Agreement under the law of England and Wales, including its effect upon what would otherwise be his rights under the current law of England and Wales and about the advantages and disadvantages, at the time the advice was provided, to Party 1 of making the Agreement;
        \item I explained to Party 1 the extent to which the Agreement is intended to influence the court's treatment of financial claims in the event of Permanent Breakdown, subject always to the court's powers regarding needs, fairness and the interests of the children.
    \end{enumerate}
\end{enumerate}

\vspace{0.8em}

\begin{tabularx}{\textwidth}{|Y|Y|}
\hline
Date & \\[0.8cm]
\hline
Signature & \\[1cm]
\hline
Name and professional capacity & \\[1cm]
\hline
Firm and address & \\[1.2cm]
\hline
\end{tabularx}

\newpage
\section*{Schedule 3A --- Certificate of Independent Specialist Legal Adviser for Party 2}

\noindent I, \rule{5cm}{0.4pt} of \rule{8cm}{0.4pt}, certify as follows:

\begin{enumerate}[label=\arabic*., leftmargin=1.8em]
    \item I am a duly qualified solicitor/barrister (delete as appropriate) of the Senior Courts of England and Wales.
    \item Prior to \PartyTwo\ entering into the Agreement between Party 2 and \PartyOne\ to which this certificate is annexed:
    \begin{enumerate}[label=(\alph*), leftmargin=1.8em]
        \item I explained to Party 2 the meaning and importance of the terms of the Agreement in such a way that I believe that she has understood them, and she confirmed to me that she does understand them;
        \item I advised Party 2 as to the effect of the Agreement under the law of England and Wales, including its effect upon what would otherwise be her rights under the current law of England and Wales and about the advantages and disadvantages, at the time the advice was provided, to Party 2 of making the Agreement;
        \item I explained to Party 2 the extent to which the Agreement is intended to influence the court's treatment of financial claims in the event of Permanent Breakdown, subject always to the court's powers regarding needs, fairness and the interests of the children.
    \end{enumerate}
\end{enumerate}

\vspace{0.8em}

\begin{tabularx}{\textwidth}{|Y|Y|}
\hline
Date & \\[0.8cm]
\hline
Signature & \\[1cm]
\hline
Name and professional capacity & \\[1cm]
\hline
Firm and address & \\[1.2cm]
\hline
\end{tabularx}

\newpage
\section*{Schedule 4 --- Relevant Statement of Party 1}

\noindent I, \PartyOne\ of \CurrentHome, state as follows:

\begin{enumerate}[label=\arabic*., leftmargin=1.8em]
    \item Prior to entering into the Agreement to which this statement is annexed, I have received or have had the opportunity to receive independent legal advice.
    \item I understand the terms of the Agreement.
    \item I understand the effect of the Agreement on my rights under the law of England and Wales.
    \item I understand the advantages and disadvantages to me in making this Agreement.
    \item I understand that, under the law of England and Wales, the court retains jurisdiction in relation to fairness, needs and the interests of the children, but that this Agreement is intended to be persuasive and to carry substantial weight if properly entered into.
\end{enumerate}

\vspace{0.8em}

\begin{tabularx}{\textwidth}{|Y|Y|}
\hline
Date & \\[0.8cm]
\hline
Signature & \\[1cm]
\hline
Name & \PartyOne \\[0.6cm]
\hline
\end{tabularx}

\newpage
\section*{Schedule 4A --- Relevant Statement of Party 2}

\noindent I, \PartyTwo\ of \CurrentHome, state as follows:

\begin{enumerate}[label=\arabic*., leftmargin=1.8em]
    \item Prior to entering into the Agreement to which this statement is annexed, I have received or have had the opportunity to receive independent legal advice.
    \item I understand the terms of the Agreement.
    \item I understand the effect of the Agreement on my rights under the law of England and Wales.
    \item I understand the advantages and disadvantages to me in making this Agreement.
    \item I understand that, under the law of England and Wales, the court retains jurisdiction in relation to fairness, needs and the interests of the children, but that this Agreement is intended to be persuasive and to carry substantial weight if properly entered into.
\end{enumerate}

\vspace{0.8em}

\begin{tabularx}{\textwidth}{|Y|Y|}
\hline
Date & \\[0.8cm]
\hline
Signature & \\[1cm]
\hline
Name & \PartyTwo \\[0.6cm]
\hline
\end{tabularx}

\end{document}
